---
title: "CMH – HTA"
subtitle: "Team Page · Real World Analytics & Accelerators (RWAA)"
date: last-modified
format:
  html:
    theme: cosmo
    toc: true
    toc-depth: 2
    toc-title: "On this page"
    smooth-scroll: true
    page-layout: full
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(dplyr)
library(reactable)
library(htmltools)

team <- readRDS("./ci_rwaa_org_v2/dat_rwaa_sa_team.rds")

cmh_hta <- team |>
  filter(ta == "cmh", fg == "hta") |>
  arrange(factor(role, levels = c("head", "lead", "member")), name)
```

## Overview

The CMH HTA team sits within the **Cardiometabolic Health (CMH)** Therapeutic Area and partners closely with Health Technology Assessment (HTA) bodies, payers, and HEOR colleagues to generate and communicate the value of Lilly's CMH portfolio.

The team supports a range of deliverables including comparative effectiveness analyses, indirect treatment comparisons (ITCs/NMAs), cost-effectiveness inputs, and evidence dossiers for HTA submissions globally — with particular focus on agencies such as NICE, G-BA, HAS, and CADTH.

---

## People

```{r people-table}
score_cols <- c("optum","health_verity","ibd_plexus","komodo","truveta","flatiron",
                "iqvia","tri_net_x","nhis","welldoc","meps","nhanes","cprd",
                "ihd","aetion","sas","r")

score_label <- function(x) {
  dplyr::case_when(x == 3 ~ "Professional", x == 2 ~ "User", TRUE ~ "")
}

display <- cmh_hta |>
  mutate(
    name       = stringr::str_to_title(stringr::str_replace_all(name, "_", " ")),
    employment = dplyr::case_when(
      emp == "ft" ~ "Full-Time",
      emp == "pt" ~ "Part-Time",
      emp == "ct" ~ "Contractor",
      TRUE        ~ emp
    ),
    role = stringr::str_to_title(role),
    across(any_of(score_cols), score_label)
  ) |>
  select(name, role, employment, any_of(score_cols))

badge_cell <- function(value) {
  if (is.na(value) || value == "") return("")
  color <- if (value == "Professional") list(bg="#ede9fe", fg="#6d28d9") else list(bg="#dbeafe", fg="#1d4ed8")
  tags$span(
    value,
    style = paste0(
      "font-size:10px;padding:1px 7px;border-radius:999px;font-weight:500;",
      "background:", color$bg, ";color:", color$fg, ";"
    )
  )
}

reactable(
  display,
  searchable       = TRUE,
  filterable       = TRUE,
  striped          = TRUE,
  highlight        = TRUE,
  defaultPageSize  = 20,
  columnGroups     = list(
    colGroup(name = "Databases", columns = intersect(score_cols[1:13], names(display))),
    colGroup(name = "Tools",     columns = intersect(score_cols[14:17], names(display)))
  ),
  columns = c(
    list(
      name       = colDef(name = "Name",       minWidth = 160, sticky = "left"),
      role       = colDef(name = "Role",       minWidth = 100, filterable = TRUE),
      employment = colDef(name = "Employment", minWidth = 110, filterable = TRUE)
    ),
    setNames(
      lapply(intersect(score_cols, names(display)), function(col) {
        colDef(
          name   = toupper(gsub("_", " ", col)),
          cell   = function(value) badge_cell(value),
          minWidth = 90
        )
      }),
      intersect(score_cols, names(display))
    )
  ),
  theme = reactableTheme(
    headerStyle      = list(background = "#185FA5", color = "#fff"),
    groupHeaderStyle = list(background = "#1e75c8", color = "#fff", fontWeight = 500)
  )
)
```

---

## Workflow

The CMH HTA team follows a structured quality workflow for all programming deliverables. The workflow applies to both **SAS/R** and **Taffy** environments and covers three roles: Primary Programmer, Independent Validator, and Peer Reviewer.

### Primary Programmer

::: {.callout-note}
Before starting any new request, review the most updated SAP and familiarise yourself with the input data and LOA.
:::

**SAS / R**

1. For any new request, create a project tracker and provide a List of Analyses (LOA) — either attached to the tracker or saved in the documentation folder.
2. LOA should always be up to date, including titles, footnotes, abbreviations, reference program names (if available), output locations/names, and any specific requirements.
3. Create folders in QA and PRD, and create a setup program (validator to peer review it). Always include the PRD path in your program header.
4. Follow best practice for program headers; include the Project Tracker ID next to the PROJECT NAME (required).
5. Run the program with no errors or warnings in the log/lst. If warnings cannot be resolved in SAS, try running via the CLUWE scheduler.
6. Carefully review the output TFL — including titles, abbreviations, footnotes, missing values, display truncation, and page breaks.
7. If a TFL is updated during validation, save a copy of the previous version and compare to ensure only necessary changes were made.
8. Once the PRD run is approved, move the LOA to PRD and e-sign.
9. Run PRD; wait for validation to complete in PRD, then e-sign.
10. Update the status and unique/final TFL counts in the project tracker.
11. For new members, update the BOW.

**Taffy**

Steps 1–2 and 5–11 follow the same process as SAS/R. Additional Taffy-specific step:

4. Create the TFL project in Taffy.

---

### Independent Validation

::: {.callout-important}
It is the validator's responsibility to determine why a mismatch exists. Only if you are convinced your result is correct should you provide the primary programmer with details of the discrepancy.
:::

**SAS / R**

1. Follow best practice for headers; include the Project Tracker ID next to the PROJECT NAME. Always include the PRD path in the program header.
2. Run the program with no errors or warnings in the log/lst. If unresolvable, try the CLUWE scheduler.
3. Confirm the primary programmer's log/lst contains no errors or warnings.
4. Confirm the big N is correctly presented in the TFL.
5. Carefully review the output TFL — titles, abbreviations, footnotes, missing values, display truncation, and page breaks.
6. If a TFL is updated during validation, save a copy of the previous version and compare.
7. Primary runs in PRD first; validator runs in PRD second.
8. E-sign both the primary and validation programs (sign as executor).
9. For new members, update the BOW.

**Taffy**

Steps 1–4 follow the same process. Additional Taffy-specific step:

5. Either the primary programmer or the validator approves the Taffy program after the primary programmer approves the PRD run.

---

### Peer Review

**SAS / R**

1. Compare the reference program with the primary program and justify any changes made. For new members: understand the meaning of each setting and the reason for any changes.
2. Carefully review the output TFL — titles, abbreviations, footnotes, missing values, display truncation, and page breaks.
3. Confirm that big N and small n are correct (recommended: write code to verify).
4. Check the log and lst files — no errors or warnings.
5. After the PRD run, confirm the QA version of the TFL approved for PRD is identical to the PRD version.
6. E-sign the primary's program on CLUWE.
7. For new members, update the BOW.

**Taffy**

Steps 1–4 follow the same process. Additional Taffy-specific step:

5. Either the primary programmer or the validator approves the Taffy program after the primary programmer approves the PRD run.

---

### Quality Checklist

Before submitting any deliverable, verify the following:

1. No hardcoding in either the main program body or output settings.
2. No footnote errors — check for wrong paths, missing abbreviations, missing LOA-requested notes, or incorrect titles.
3. The validation lst file is complete, including available compare results.
4. Input data has been checked against the LOA; consult the primary programmer on how to handle missing data.
5. No missing rows, columns, or values in the TFL output.
6. Program header follows good practice guidelines.
7. Program footnotes follow good practice guidelines.
8. Verify the necessity of all variables in the analysis model.
9. Verify the necessity of all parameters in the DM table.
10. Table conveys clear information — e.g. Y/N → Yes/No, F/M → Female/Male.
11. Check convergence type in both QA and PRD environments.
12. Notes are made throughout the program and in the LOA for any updates.
13. Programs are executed in the correct order.
14. Pay attention to rounding issues that may cause incorrect patient categorisation.
15. Pay attention to timepoints and populations when using reference code — parameters may differ from the reference.
16. For independent validations, the primary programmer and validator must not see each other's code.
17. When creating a customised ADaM dataset, write a corresponding specification.

---

*Content or technical issues with this site? [Click here](maintenance.qmd) to report any issues or provide feedback.*
